---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---
## Introduction
It is now possible to collect a large amount of data about personal movement using activity monitoring devices such as a Fitbit, Nike Fuelband, or Jawbone Up. These type of devices are part of the “quantified self” movement – a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. But these data remain under-utilized both because the raw data are hard to obtain and there is a lack of statistical methods and software for processing and interpreting the data.



## Loading and preprocessing the data
```{r}
if (!file.exists("activity.csv") )
{
  dlurl <- 'http://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip'  
  download.file(dlurl,destfile='repdata%2Fdata%2Factivity.zip',mode='wb')  
  unzip('repdata%2Fdata%2Factivity.zip')
}
```
# Read data
```{r}
data <- read.csv("activity.csv")
```
## What is mean total number of steps taken per day?
```{r}
steps_<-aggregate(steps~date,data,sum)
hist(steps_$steps)
rmean <- mean(steps_$steps)
rmean
rmedian <- median(steps_$steps)
rmedian

```
## What is the average daily activity pattern?
```{r}
steps_i<-aggregate(steps~interval,data,sum)
plot(steps_i$interval,steps_i$steps,type="l")
max_interval<-steps_i[which.max(steps_i$steps),1]
max_interval
```

## Imputing missing values
```{r}
NATotal <- sum(!complete.cases(data))
NATotal
StepsAverage <- aggregate(steps ~ interval, data = data, FUN = mean)
fillNA <- numeric()
for (i in 1:nrow(data)) {
  obs <- data[i, ]
  if (is.na(obs$steps)) {
    steps <- subset(StepsAverage, interval == obs$interval)$steps
  } else {
    steps <- obs$steps
  }
  fillNA <- c(fillNA, steps)
}
new_activity <- data
new_activity$steps <- fillNA
StepsTotalUnion <- aggregate(steps ~ date, data = new_activity, sum, na.rm = TRUE)
hist(StepsTotalUnion$steps, main = paste("Total Steps Each Day"), col="blue", xlab="Number of Steps")
```
#Create Histogram to show difference. 
```{r}
plot(steps_$steps, main = paste("Total Steps Each Day"), col="green", xlab="Number of Steps", add=T)
legend("topright", c("Imputed", "Non-imputed"), col=c("blue", "green"), lwd=10)
rmeantotal <- mean(StepsTotalUnion$steps)
rmeantotal
rmediantotal <- median(StepsTotalUnion$steps)
rmediantotal
rmediandiff <- rmediantotal - rmedian
rmediandiff
rmeandiff <- rmeantotal - rmean
rmeandiff

```
## Are there differences in activity patterns between weekdays and weekends?
```{r}
weekdays <- c("Monday", "Tuesday", "Wednesday", "Thursday", 
              "Friday")
new_activity$dow = as.factor(ifelse(is.element(weekdays(as.Date(new_activity$date)),weekdays), "Weekday", "Weekend"))
StepsTotalUnion <- aggregate(steps ~ interval + dow, new_activity, mean)
library(lattice)
xyplot(StepsTotalUnion$steps ~ StepsTotalUnion$interval|StepsTotalUnion$dow, main="Average Steps per Day by Interval",xlab="Interval", ylab="Steps",layout=c(1,2), type="l")
```

